Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
adjusted the structure of section Methodology

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow buildings based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\subsection{Aggregating close buildings by adding bridges}
\label{sec:Merge}

At time $t=1$, we know that 
which buildings will finally be aggregated into the same built-up area
(see \sect\ref{sec:Group}).
We connect each pair of these buildings by adding a line segment linking the 
nearest points.
These line segments may cross each other or even intersect buildings.
To make the topology simple, 
we only select some of the line segments as bridges.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are identified as bridges.

At any time $t$, some of the identified bridges are picked to aggregate 
buildings 
which grow to become too close.
The buildings and the bridges already comprise some MSTs.
We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
We do not introduce bridges according to nearest points at time $t$
because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
example).

\begin{figure}[tb]
	\centering
	\includegraphics[]{NearestPoints}
	\caption{The nearest points between a pair of buildings may change because 
	of growing. 
		The two squares and the two circles respectively mark
		the nearest points before and after growing.
	}
	\label{fig:NearestPoints}
\end{figure}

\subsection{Simplifying grown buildings}
\label{sec:Simplify}
\citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the directions of the buildings have to be 
concerned.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
We use a method based on buffering to remove pits and spikes of buildings.
Our method is slightly different than \citet{Meijers2016},
but there is an available library \textsc{Clipper} \citep{Johnson2014} 
for the operations.
\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

After carrying out the dilation-erosion-dilation method, 
we simplify the buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
There are many research works about grouping buildings.
\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
However, our two needs, 
the distances between buildings are always larger than a specified threshold 
and small bays should be removed, 
motivate us to develop our own grouping method.

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$
(We will talk about how to define $\dtrm{C}$ later).
If two buffers overlap, 
then the original buildings are put in the same group.

\begin{figure}[tb]
	\centering
	\includegraphics[]{CloseDetect}
	\caption{bla.}
	\label{fig:CloseDetect}
\end{figure}

Now we show how to define distance $\dtrm{C}$, 
which is used to detect closeness.
The distance between two buildings on a map should be larger than a threshold.
Following \citet{Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
	\label{eq:d_epsilont}
	d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

%(see \fig\ref{fig:RemoveBay} for example).
As stated in \sect\ref{sec:Simplify}, 
we wish to remove ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may come from a complex original building,
or from bridging some buildings.
\fig\ref{fig:RemoveBay}e shows an example of the later case.
To remove a bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
For the buildings in \fig\ref{fig:RemoveBay}a,
the final result of removing a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each original building with distance 
		$\dtrm{G}+\dtrm{D}$.		
		(c) Erode the dilated polygons with distance $\dtrm{D}$.
		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
		If two polygons in (d) intersect, 
		the original buildings will be put in the same group 
		because they will become too close at time $t$.
		There are two groups according to (d).
		One consists of the single middle building and 
		the surrounding $9$ buildings comprise the other group.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

\subsection{Generating the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We group (see \sect\ref{sec:Group}) 
and merge (see \sect\ref{sec:Merge}) buildings on start map.
Then we grow (see \sect\ref{sec:Grow}) 
and simplify (see \sect\ref{sec:Simplify}) the merged buildings.
See for example \fig\ref{fig:Buffer_MiterLimits}, 
the building at time $t=1$ is the goal form of the three buildings of $t=0$.

>>>>

\subsection{Growing buildings by buffering}
\label{sec:Grow}
We grow buildings based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

\subsection{Simplifying grown buildings based on dilation and erosion}
\label{sec:DilationErosion}
\citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the directions of the buildings have to be 
concerned.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
We use a method based on buffering to remove pits and spikes of buildings.
Our method is slightly different than \citet{Meijers2016},
but there is an available library \textsc{Clipper} \citep{Johnson2014} 
for the operations.
\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

\subsection{Iteratively aggregating close buildings by adding bridges}
\label{sec:Aggregate}

We grow each original building and, as illustrated in 
\sect\ref{sec:DilationErosion}, simplify the grown building.
If some buildings become too close after these operations,
we aggregate them by adding bridges.
Following \citet{Stoter2009}, 
we define that two buildings are too close if their distance is less than
$\epsilon= 0.2\,\mathrm{mm}$ on map.
The real separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

Our way of detecting close buildings is simple.
We buffer buildings with distance $d_{\epsilon, t}/2$ using round joins.
We merge the buffers that overlap each other.
The buildings intersect with the same merged buffer 
are identified as a group of close buildings.
According to the group of buildings, 
we find the group of corresponding original buildings.
For each pair of the original buildings in a group,
we connect them by adding a line segment linking the nearest points.
The line segments for the group of original buildings may cross each other or 
even intersect buildings.
To make the topology simple, 
we only select some of the line segments as \emph{bridges}.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are identified as bridges.
We aggregate the group of original buildings by adding these bridges.

Notice that after growing the additional bridges may be too close to buildings 
from another group.
We iteratively aggregate buildings.
This time we grow the original buildings with bridges.
Similar to what we do before, we aggregate buildings by introducing bridges.
We stop this iteration until the number of group does not decrease anymore.

%At any time $t$, some of the bridges are picked to aggregate buildings 
%which grow to become too close.
%The buildings and the bridges already comprise some MSTs.

%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%\begin{equation}
%\label{eq:d_epsilont2}
%d_{\epsilon, t} = \epsilon \cdot M_t.
%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap with each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{NearestPoints}
%	\caption{The nearest points between a pair of buildings may change because 
%		of growing. 
%		The two squares and the two circles respectively mark
%		the nearest points before and after growing.
%	}
%	\label{fig:NearestPoints}
%\end{figure}

\subsection{Simplifying buildings using Imai--Iri algorithm}
\label{sec:ImaiIri}

We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.

We simplify the buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
First, this algorithm finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline 
and has the least number of line segments, with error smaller than $d_{l,t}$.

@@

%\subsection{Grouping buildings based on buffering}
%\label{sec:Group}
%There are many research works about grouping buildings.
%\citet{Cetinkaya2015} and \citet{Deng2017} compared some of the methods.
%However, our two needs, 
%the distances between buildings are always larger than a specified threshold 
%and small bays should be removed, 
%motivate us to develop our own grouping method.
%
%Original buildings grow according to time $t$.
%We put the original buildings in the same group if 
%they grow so that their distance is less than $d_{\epsilon, t}$.
%Following \citet{Stoter2009}, 
%we set the threshold $\epsilon= 0.2\,\mathrm{mm}$ on map. 
%The real separation threshold at time $t$ is
%%\begin{equation}
%%\label{eq:d_epsilont}
%%d_{\epsilon, t} = \epsilon \cdot M_t.
%%\end{equation}
%We group buildings based on buffering.
%The basic idea is that 
%we buffer the original buildings with distance $\dtrm{G}$
%and an additional distance $d_{\epsilon, t}/2$
%(the distance between two buildings should be at least $d_{\epsilon, t}$).
%If two buffers overlap, 
%then the original buildings are put in the same group.
%However, as some parts of a building grow faster than other parts, 
%this basic idea may cause problems.
%An example is shown in \fig\ref{fig:CloseDetect}c and~d.
%In \fig\ref{fig:CloseDetect}d, 
%the buffers of buildings $p$ and $q$ overlap each other.
%So we should aggregate buildings $p$ and $q$ at time $t$
%because they will grow to become too close.
%According to the bridges in \fig\ref{fig:CloseDetect}b, 
%buildings $p$ and $q$ should be aggregated via building $r$.
%Unfortunately, neither $p$ or $q$ will be too close to $r$.
%As we use bridges to aggregate buildings 
%(see \sect\ref{sec:Aggregate}),
%we are not able to aggregate buildings $p$ and $q$. 
%To avoid this situation, 
%we buffer original buildings with distance
%$\alpha \dtrm{G}+d_{\epsilon, t}/2$ using round joins.
%This buffering guarantees 
%that every part of a building grows with the same speed.
%If the buffers of two buildings overlap with each other,
%then the two buildings are surely aggregated into one.
%Using this buffering, in most of cases 
%two buildings are aggregated as soon as 
%their separation distance is less than 
%$2(\alpha -1) \dtrm{G}+d_{\epsilon, t}$.
%The advantage is that we guarantee that 
%any two buildings have separate distance less than $d_{\epsilon, t}$ will be 
%aggregated via bridges.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics[]{CloseDetect}
%	\caption{Group buildings based on buffering.
%		(a) original buildings.
%		(b) bridges detected to aggregate the three buildings.
%		(c) grow the original buildings with distance $\dtrm{G}$.
%		(d) buffer the grown buildings in (c) 
%		with distance $d_{\epsilon, t} /2$ using round joins.
%		(e) buffer the original buildings 
%		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
%		using round joins, where $\alpha=1.5$
%		(see \sect\ref{sec:Grow}).
%		(f) according to the buffer in (e), 
%		we put the three original buildings in the same group.
%		We aggregate the original buildings by adding the two bridges 
%		and grow the aggregated building with distance $\dtrm{G}$.
%	}
%	\label{fig:CloseDetect}
%\end{figure}

%
%As stated in \sect\ref{sec:DilationErosion}, 
%we wish to remove ``bays'' 
%which have widths less than $2 \dtrm{D}$.
%A bay may come from a complex original building,
%or from bridging some buildings.
%\fig\ref{fig:RemoveBay}e shows an example of the later case.
%To remove a bay,
%we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
%and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
%with distance $\dtrm{D}$.
%There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
%so we iteratively group until the number of groups does not decrease.
%For the buildings in \fig\ref{fig:RemoveBay}a,
%the final result of removing a bay is the outer polygon of 
%\fig\ref{fig:RemoveBay}h. 
%In comparison, the result is \fig\ref{fig:RemoveBay}e 
%if we do not dilate (setting $\dtrm{D}=0$) to remove a bay.
%Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
%kind of bay and will be removed by overgrowing.
%
%
%\begin{figure*}[tb]
%	\centering
%	\includegraphics[draft=false]{RemoveBay}
%	\caption{Group buildings iteratively.
%		(a) Original buildings.
%		(b) Dilate each original building with distance 
%		$\dtrm{G}+\dtrm{D}$.		
%		(c) Erode the dilated polygons with distance $\dtrm{D}$.
%		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
%		If two polygons in (d) intersect, 
%		the original buildings will be put in the same group 
%		because they will become too close at time $t$.
%		There are two groups according to (d).
%		One consists of the single middle building and 
%		the surrounding $9$ buildings comprise the other group.
%		(e) The result of growing and merging at time $t$ 
%		if we use $\dtrm{D}=0$.
%		The process of (f), (g), and (h) is similar to 
%		that of (b), (c), and (d).		
%		The difference is that 
%		instead of applying the operators to each single building, 
%		we do that for the buildings in the same group.
%		In (f), we manage to remove the bay in (e) by additionally dilating 
%		with distance $\dtrm{D}$.
%		There is only one group left according to (h).
%		We iteratively group buildings in this way until the number of groups 
%		does not decrease.
%	}
%	%in this example, we used _dblTotalGrow *= 5;
%	\label{fig:RemoveBay}
%\end{figure*}

\subsection{Generating the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We group (see \sect\ref{sec:Group}) 
and merge (see \sect\ref{sec:Aggregate}) buildings on start map.
Then we grow (see \sect\ref{sec:Grow}) 
and simplify (see \sect\ref{sec:DilationErosion}) the merged buildings.
See for example \fig\ref{fig:Buffer_MiterLimits}, 
the building at time $t=1$ is the goal form of the three buildings of $t=0$.
